Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2018-12-26 cikm2016/cikm_dateparse.tex
Expose true identities.
Convert to Tableau copyright and style.
Convert DOI to  Tableau Technical Note
Updated into technical report

%\documentclass{acm_proc_article-sp}
%\documentclass[conference]{IEEEtran}
\documentclass{sig-alternate-05-2015}
%
\usepackage{url}
\usepackage{syntax}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{mathtools}
\usepackage{color}
\usepackage{caption} 
\usepackage{tikz}
\usepackage{enumitem}
\captionsetup[table]{skip=10pt}

@@

%
\begin{document}

\title{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}
\input{anonymous}

\maketitle

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003227.10003351.10003218</concept_id>
<concept_desc>Information systems~Data cleaning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10002952.10003219.10003215</concept_id>
<concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002951.10002952.10003219.10003223</concept_id>
<concept_desc>Information systems~Entity resolution</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003317.10003347.10003352</concept_id>
<concept_desc>Information systems~Information extraction</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010179.10010182</concept_id>
<concept_desc>Computing methodologies~Natural language generation</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Data cleaning}
\ccsdesc[300]{Information systems~Extraction, transformation and loading}
\ccsdesc[300]{Information systems~Entity resolution}
\ccsdesc[300]{Information systems~Information extraction}
\ccsdesc[300]{Computing methodologies~Natural language generation}%

%
%  Use this command to print the description
%
\printccsdesc

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{dateparse}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ``.bib'' file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

>>>>

\documentclass[10pt,twoside,a4paper,twocolumn]{article}
\usepackage[left=1.75cm, right=1.75cm, top=2cm]{geometry}
\setlength\columnsep{20pt}

%

\usepackage{url}
\usepackage{syntax}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\usepackage{mathtools}
\usepackage{color}
\usepackage{caption} 
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{hyperref}
\captionsetup[table]{skip=10pt}

@@

\setlength{\tabcolsep}{4pt}   % set length to -2pt
%
\begin{document}

%\input{authors}

%\maketitle

\begin{titlepage}
   \begin{center}
       \vspace*{1cm}
  \includegraphics[width=0.3\textwidth]{figures/tableau}
     \vspace*{1cm}

        \Large       
 \textbf{Does Anybody Really Know What Time It Is?\\
Automating the Extraction of Date Scalars}\\
 TR \#2018-01
       \vspace{1cm}

\large
\textbf{Richard Wesley\\
Vidya Setlur\\
Dan Cory} 
     %  \vfill

       \vspace{2cm}
 Tableau Software\\
     1621 North 34th Street\\
      Seattle, WA 98103\\  
 \vspace{2cm}
 \small
Copyright \copyright 2018\\
Tableau Software All rights reserved.\\
The information contained in this document is the exclusive property of Tableau.
This work is protected under United States copyright law and other international copyright treaties and conventions.No part of this work may be reproduced, used, or transmitted in any form or by any means except as expressly permitted in writing by Tableau.\\
All requests should be sent to Attention: Tableau Legal \href{mailto:legal@tableau.com}{legal@tableau.com} 
 \end{center}
\end{titlepage}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10002951.10003227.10003351.10003218</concept_id>
%<concept_desc>Information systems~Data cleaning</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10002951.10002952.10003219.10003215</concept_id>
%<concept_desc>Information systems~Extraction, transformation and loading</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10002951.10002952.10003219.10003223</concept_id>
%<concept_desc>Information systems~Entity resolution</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10002951.10003317.10003347.10003352</concept_id>
%<concept_desc>Information systems~Information extraction</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10010147.10010178.10010179.10010182</concept_id>
%<concept_desc>Computing methodologies~Natural language generation</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Information systems~Data cleaning}
%\ccsdesc[300]{Information systems~Extraction, transformation and loading}
%\ccsdesc[300]{Information systems~Entity resolution}
%\ccsdesc[300]{Information systems~Information extraction}
%\ccsdesc[300]{Computing methodologies~Natural language generation}%

%
%  Use this command to print the description
%
%\printccsdesc

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
%\bibliographystyle{abbrv}
\bibliography{dateparse}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ``.bib'' file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
